Case Study: ChIP-seq Differential Peak Calling (csaw)

### 2018-04-04 datasets/ChIP-seq/ChIPseq-h3k4me3-csaw.Rmd
Fix error in chr filtering: hs not mm

The _csaw_ package provides a powerful and flexible approach to differential peak calling
based on counting reads in sliding windows across the genome. Unlike the _DiffBind_ approach
which restricts testing to peaks called from the same samples, the sliding window approach
is able to detect differential peaks over sharper or wider regions, without being constrained
by the original peak boundaries obtained from the peak calling algorithm, e.g. _MACS_.
Differential peaks are called at each window using _edgeR_ and p-values are combined within
adjacent windows (clusters).

@@

We download the fastq files directly from the UCSC ENCODE portal and align them against the reference.

@@

We also use the GRCh38 reference genome used for ENCODE3 analysis. If the reference index is
not already available, we must first download the reference file. Note that this is a different
reference than what was originally used for the data.

@@

```{r}
std_chr <- paste0("chr", c(1:19, "X", "Y"))
param <- readParam(minq = 20, discard = bl, restrict = std_chr)
```

>>>>

The _csaw_ package provides a powerful and flexible approach to differential peak calling
based on counting reads in sliding windows across the genome. The sliding window approach
allows for the detection of differential peaks over sharper or wider regions, without being
constrained by the original peak boundaries obtained from the peak calling algorithm, e.g. _MACS_.
Differential peaks are called at each window using _edgeR_ and p-values are combined within
adjacent windows (clusters).

@@

We download the fastq files directly from the UCSC ENCODE portal.

@@

We use the GRCh38 reference genome used in the ENCODE3 analysis. If the reference index is
not already available, we must first download the reference file. Note that this is a different
reference than what was originally used for the data in earlier analyses of the ENCODE project.

@@

```{r}
std_chr <- paste0("chr", c(1:22, "X", "Y"))
param <- readParam(minq = 20, discard = bl, restrict = std_chr)
```
